Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}
%\newcommand{\todo}[1] {}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We show results on both the 
downsampled and non-downsampled data sets.

@@

%\paragraph{Internal validity}
 The authors used 
 Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
 usage of machine learning algorithms to analyze our datasets. We are aware that, 
 as every human written tool, Weka is prone to contain errors and/or bugs; 
 nonetheless, Weka is a broadly used, open source tool that is subject to high 
 quality standards and a vast user and developer base which makes it more likely 
 to be a high quality code and to have less bugs than lesser used tools.

@@

%\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
 build the notion that since we are building our analysis on top of a vast 
 data set, the threat of this analysis 
 not generalizing to other projects is mitigated.

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.

\section{Conclusion}
In this study we have analyzed how technical and social factors can be used to
predict high quality contributions.  We have found that these factors provide
insight when predicting the success of a build with a technical factors leading
to a 14\% increase in predictive power, and another 12\% increase when
incorporating social factors into the prediction.

>>>>

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}

%\newcommand{\todo}[1] {}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train on the down-sampled data but show results on both 
downsampled and non-downsampled data sets.\todo{CLG says: that last sentence is
  true, right?}

@@

%\paragraph{Internal validity}
We use Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, a well known machine-learning tool,
to analyze our data.
Like all tools, Weka is prone to contain errors and/or bugs. 
Nonetheless, Weka is a well-known used, open source tool, and as such is likely
to be of relatively high quality, mitigating threats to internal validity.

@@

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.\todo{...and?  Something
   like ``future work remains to assess the degree of these threats'' will do.}

\section{Conclusion}

We have analyzed how technical and social factors can be used to
predict high quality open source contributions, as measured by continuous
integration build success.  We have found that these factors provide
insight when predicting the success of a build with a technical factors leading
to a 14\% increase in predictive power, and another 12\% increase when
incorporating social factors into the prediction.
